---
title: "ANCOVA"

output: pdf_document
---

```{r}
library(lsmeans)
library(car)
library(multcompView)
library(lme4)
library(lmerTest)
library(aplpack)
library(ggplot2)
library(vioplot)
library(bit64)
library(olsrr)
library(lmtest)
library(goftest)
library(MASS)
## Warning: package 'lmtest' was built under R version 3.6.3
## Loading required packag
data<-read.csv("merged_mean_aggregated.csv")
options("scipen"=99)
```

# Filter Out Relevant Data

```{r}
data<-subset(data, select = c(safegraph_place_id,vistor_census_block,COVID_Start, minorityportion,MEDIAN.INCOME,census_block_classification,dist,mean_monthly_visitations))
```


```{r}
data
```

# Built the ANCOVA model

```{r}
## fit model
fit.ANCOVA=aov((mean_monthly_visitations)~(COVID_Start)+minorityportion+MEDIAN.INCOME+dist+(census_block_classification)+(COVID_Start):minorityportion+(COVID_Start):MEDIAN.INCOME+(COVID_Start):dist+(COVID_Start):(census_block_classification)
             +minorityportion:MEDIAN.INCOME+minorityportion:dist+minorityportion:(census_block_classification)
             +MEDIAN.INCOME:dist+MEDIAN.INCOME:(census_block_classification)+
               dist:(census_block_classification),data=data)
```

# Test the assumptions to see if they fit   

BP test: Test for heteroskedasticity (acceptable if $p-value<0.05$)  
Anderson Darling Test: Test for normality (acceptable if $p-value<0.05$)  

```{r}
ad.test(studres(fit.ANCOVA))
bptest(fit.ANCOVA)
```


Assumptions okay. Move on to results  

```{r}
## ANOVA table
anova(fit.ANCOVA)
```

 
# Make the neccessary Plots  
 
## Changes in visitation due to COVID plot

```{r}
mynames<-c("pre-COVID", "COVID")
vioplot(data$mean_monthly_visitations~data$COVID_Start, names=mynames,ylab="mean monthly visitations", xlab="COVID-era")
```
## Census block urban classification and changes due to COVID  

```{r}
one<-data[which(data$COVID_Start=="True"),]
two<-data[which(data$COVID_Start=="False"),]
vioplot(one$mean_monthly_visitations~one$census_block_classification, data=one, col = "palevioletred", plotCentre = "line", side = "right", xlab="Census block classification", ylab="mean monthly visitations")
vioplot(two$mean_monthly_visitations~two$census_block_classification, data=two, col = "lightblue", plotCentre = "line", side = "left", add = T)
#title(xlab = "Census Classification type", ylab = "Mean monthly visitations")
legend("topleft", fill = c("lightblue", "palevioletred"), legend = c("pre-covid", "covid"))
```
## Changes to visitations to national parks amidst COVID19 based on diversity of Census Block Groups  

```{r}

ggplot(data = data, aes(x = minorityportion, y = mean_monthly_visitations, color = COVID_Start)) +
        geom_smooth(method = "lm") +
        labs(title = "",
             x = "minority portion from visitor census block group",
             y = "mean monthly visitations", color="COVID/pre-covid era")+scale_color_discrete(labels = mynames)
```

## Changes to visitations to national parks amidst COVID19 based on distance from Census Block Groups  

```{r}

ggplot(data = data, aes(x = dist, y = mean_monthly_visitations, color = COVID_Start)) +
        geom_smooth(method = "lm") +
        labs(title = "",
             x = "distance from visitor census block group",
             y = "mean monthly visitations", color="COVID/pre-covid era")+scale_color_discrete(labels = mynames)
```
## Changes to visitations to national parks amidst COVID19 based on Median Income of Census Block Groups  


```{r}

ggplot(data = data, aes(x = MEDIAN.INCOME, y = mean_monthly_visitations, color = COVID_Start)) +
        geom_smooth(method = "lm") +
        labs(title = "",
             x = "Median income from vistors census block group",
             y = "mean monthly visitations", color="COVID/pre-covid era")+scale_color_discrete(labels = mynames)
```